Robust and Efficient CSI Compression Using CLLWCsiNet in Noisy MIMO Environments

### 2025-04-06 paper_latex_edit - Copy.tex
✅ Citation-rich Quantization Adaptor for Bit-Level Deep Learning-Based Massive MIMO CSI Feedback

@@

>>>>

Zhang et al. \cite{zhang2022quantization} addresses the critical challenge of quantization in deep learning-based CSI feedback for massive MIMO systems. The authors propose an innovative adaptor-assisted quantization strategy that significantly improves feedback efficiency while maintaining reconstruction accuracy.

@@

	\bibitem{zhang2022quantization}
	X. Zhang, Z. Lu, R. Zeng, and J. Wang,
	``Quantization Adaptor for Bit-Level Deep Learning-Based Massive MIMO CSI Feedback,''
	arXiv preprint arXiv:2211.02937v2, 2022.
